---
title: "Troubleshooting, Tables, and More Wrangling"
author: "Scout Leonard"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(lubridate)
library(kableExtra)
library(janitor)
```

### janitor::get_dupes()
returns duplicated observations (any rows where everything is the same across all variables?)

checks for all columns unless specified as otherwise
```{r}
starwars_dupes <- get_dupes(starwars)

starwars_dupes_names <- starwars %>% 
  get_dupes(name)

starwars_dupes_eye_color <- starwars %>% 
  get_dupes(eye_color, hair_color)

starwars_dupes_eye_color
#tells how many rows exist for observations with the same eye color and hair color
```
### dplyr::across()

dplry::across() allows you to perform functions across multiple comuns that you specify 

```{r}
#convert anything that is a character into lowercase
sw_across <- starwars %>% 
  mutate(across(where(is.character), tolower))

sw_across
```


```{r}
starwars %>% 
  group_by(homeworld) %>% 
  summarize(across(where(is.numeric), mean, na.rm = TRUE))

#NaN comes from 0/0 values 
#you can also give across a range of collumns using across(col_a:col_b, function)
```

### basic / common troubleshooting stuff 

```{r}
starwars %>% 
  filter(homeworld == "Naboo")
```

```{r}
starwars %>% 
  separate(skin_color, into = c("col_1", "col_2"), sep = ",")
```

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point()
```


```{r}
#convert all numeric data to character data
#fct_relevel lets you change the order of variables
#unite is the opposite if separate! bring tog columns! 
troubleshooting <- penguins %>% 
  mutate(across(where(is.numeric), as.character)) %>%
  mutate(island = fct_relevel(island, c("Dream", "Biscoe", "Torgersen"))) %>% 
  unite(island_yr, c(island, year), sep = "_") %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  relocate(island_yr, .after = species) %>% 
  rename(penguin_spp = species)

```

Reprex needs to be totally self contained. This means libraries should be included in the code. 
Make a simple dataset! We use tribble here :)

Select code, copy to clipboard, run reprex in the console! 

Don't run it again, because your reprex gets copied to your clipboard after running.
```{r}
library(tidyverse)

df <- tribble(
  ~name, ~height, ~hair_color,
  "Teddy", 2.2, "brown",
  "Khora", 3.1, "white",
  "Waffle", 1.0, "tan"
)

df %>% 
  filter(name == "Waffle")


```






